---
title: "Project 3: state302util Tutorial"
author: "Junxi Liao"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{state302util Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(stat302util)
```

# Introductory
The package \code{stat302util} contains the functions that are taught and built 
in the STAT302 course. The functions contained make inferences and/or
predictions based on the input data. Namely, this package has the ability to 
perform a t-test, to fit linear models, to find the k-nearest neighbor cross-
validatory classification, and to make random forest cross-validation 
prediction. 

This package is built following Bryan D Martin's instruction from 
\link[https://bryandmartin.github.io/STAT302/docs/LectureSlides/lectureslides9/lectureslides9.html#1]. 


Install \texttt{stat302util} using:
```{r}
devtools::install_github("hugoliao330/stat302util", build_vignette = TRUE, build_opts = c())
library(stat302util)
# Use this to view the vignette in the Demo HTML help
help(package = "stat302util", help_type = "html")
# Use this to view the vignette as an isolated HTML file
utils::browseVignettes(package = "stat302util")
```






